### 2025-06-22 modern-portfolio-theory.qmd
20250622 - clarifying text

@@

@@

The formula for the variance (and standard deviation) of the sum of two variables is in @eq-varianceSumTwoVars:

@@

@@

@@

@@

@@

@@

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = team_name)) +
  #geom_text(
  #  hjust = 0,
  #  vjust = 0) +
  #geom_smooth() +
  coord_cartesian(
    xlim = c(NA,NA),
    ylim = c(NA,NA),
    expand = TRUE) +
  labs(
    x = "Standard Deviation of Players' Projected Fantasy Points (Season) Across Sources",
    y = "Mean of Players' Projected Fantasy Points (Season) Across Sources",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

@@

>>>>

A scatterplot of the expected returns versus risk, based on projected fantasy points, is in @fig-projectedPointsMeanVsSD.

@@

A scatterplot of the expected returns versus risk, based on projected fantasy points, is in @fig-projectedPointsMeanVsSDPDF.

@@

Now let's consider the expected returns versus risk for a combination of players.
The formula for the variance (and standard deviation) of the sum of two variables is in @eq-varianceSumTwoVars:

@@

Below is code for obtaining the expected returns and risk for various combinations of Quarterback, Running Back, and Wide Receiver.

@@

Now let's generate the efficient frontier across all players.

@@

A scatterplot of the expected returns versus risk, based on weekly fantasy points, is in @fig-fantasyPointsMeanVsSD.

@@

A scatterplot of the expected returns versus risk, based on weekly fantasy points, is in @fig-fantasyPointsMeanVsSDPDF.

@@

Now let's consider the expected returns versus risk for a combination of players.
Below is code for obtaining the expected returns and risk for various combinations of Quarterback, Running Back, and Wide Receiver.

@@

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = team_name)) +
  #geom_text(
  #  hjust = 0,
  #  vjust = 0) +
  #geom_smooth() +
  coord_cartesian(
    xlim = c(NA,NA),
    ylim = c(NA,NA),
    expand = TRUE) +
  labs(
    x = "Standard Deviation of Players' Fantasy Points From Week-to-Week",
    y = "Mean of Players' Fantasy Points Across Weeks",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

Now let's generate the efficient frontier across all players.

@@

In these examples, we have computed the efficient frontier across *all* players.
However, it would be more relevant to establish the efficient frontier for the possible combinations of players (e.g., one Quarterback, two Running Backs, two Wide Receivers, one Tight End, one Kicker, etc.).
Nevertheless, the above examples illustrate how one might do this; one could extend the examples to consider whole teams rather than just three players at a time.
